An Evolutionary Algorithm for the Multiobjective Risk-Equity Constrained Routing Problem

### 2011-11-29 DAW_hazmatHypE/trunk/paper/hazmatRouting_EvolOptim.tex
minor changes in description of instances

\subsection{Differences Between Instances}
The basis for our experiments are three instances of the lazio network with 2 (lazio\_2), 3 (lazio\_3), and 4 commodities (lazio\_4\_1) which differ also differ in the number of trucks for the commodities. Whereas the number of trucks for lazio\_3 and lazio\_4\_1 have been chosen randomly, lazio\_2 has the same number of trucks than the lazio\_3 instance for the first two commodities.

>>>>

\subsection{Differences Between Instances}
The basis for our experiments are 5 instances of the lazio network with 2 (lazio\_2), 3 (lazio\_3), and 4 commodities (lazio\_4\_1, lazio\_4\_2, and lazio\_4\_3) which differ also in the number of trucks for the commodities. Whereas the number of trucks for lazio\_3 and lazio\_4\_1 have been chosen randomly, lazio\_2 has the same number of trucks than the lazio\_3 instance for the first two commodities. The lazio\_4\_2 instance has only 1 truck more for commodity 4 than lazio\_4\_1 and overall three times the number of trucks for each commodity than the instance lazio\_4\_3.
